Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-07-20 submission/Sze_Obesity_mBio_2016.tex
Run rules for submission on axiom

\textbf{\emph{Literature Review and Study Inclusion.}} To perform a
robust meta-analysis and limit inclusion bias, we followed the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines to identify the studies that we analyzed (14). A detailed
description of our selection process and the exact search terms are
provided in the Supplemental Text and in Figure 1. Briefly, we searched
PubMed for original research studies that involved studying obesity and
the human microbiome. The initial search yielded 187 studies. We
identified 10 additional studies that were not designed to explicitly
test for an association between the microbiome and obesity. We then
manually curated the 197 studies to select those studies that included
BMI and 16S rRNA gene sequence data. This yielded 11 eligible studies.
An additional study was removed from our analysis because no individuals
in the study had a BMI over 30. Among the final 10 studies, 3 were
identified from our PubMed search (10, 15, 16), 5 were originally
identified from the 10 studies that did not explicitly investigate
obesity but included BMI data (17--21), and two datasets were used (22,
23) because these publications did not specifically look for any
metabolic or obesity conditions but had control populations and enabled
us to help mitigate against publication biases associated with the
bacterial microbiome and obesity. The ten studies are summarized in
Table 1. For comparison, two of these studies were included in the
Finucane re-analysis study (10, 21) and four of these studies were
included in the Walters re-analysis study (10, 15, 20, 21). The 16S rRNA
gene sequence data from each study was re-analyzed using a similar
approach based on previously described methods for reducing the number
of chimeric sequences and sequencing errors for 454 and Illumina MiSeq
data (24, 25). The sequences were clustered into operational taxonomic
units (OTUs) using the average neighbor approach (26) and into taxonomic
groupings based on their classification using a naive Bayesian
classifier (27).

@@

>>>>

\textbf{\emph{Literature Review and Study Inclusion.}} To perform a
robust meta-analysis and limit inclusion bias, we followed the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines to identify the studies that we analyzed (14). A detailed
description of our selection process and the exact search terms are
provided in the Methods section and in Figure 1. Briefly, we searched
PubMed for original research studies that involved studying obesity and
the human microbiome. The initial search yielded 187 studies. We
identified 10 additional studies that were not designed to explicitly
test for an association between the microbiome and obesity. We then
manually curated the 197 studies to select those studies that included
BMI and 16S rRNA gene sequence data. This yielded 11 eligible studies.
An additional study was removed from our analysis because no individuals
in the study had a BMI over 30. Among the final 10 studies, 3 were
identified from our PubMed search (10, 15, 16), 5 were originally
identified from the 10 studies that did not explicitly investigate
obesity but included BMI data (17--21), and two datasets were used (22,
23) because these publications did not specifically look for any
metabolic or obesity conditions but had control populations and enabled
us to help mitigate against publication biases associated with the
bacterial microbiome and obesity. The ten studies are summarized in
Table 1. For comparison, two of these studies were included in the
Finucane re-analysis study (10, 21) and four of these studies were
included in the Walters re-analysis study (10, 15, 20, 21). The 16S rRNA
gene sequence data from each study was re-analyzed using a similar
approach based on previously described methods for reducing the number
of chimeric sequences and sequencing errors for 454 and Illumina MiSeq
data (24, 25). The sequences were clustered into operational taxonomic
units (OTUs) using the average neighbor approach (26) and into taxonomic
groupings based on their classification using a naive Bayesian
classifier (27).

@@

\textbf{\emph{In-Depth Overview of Search Strategy.}} The initial search
strategy included looking for all papers that initially fit under the
below NCBI PubMed advanced search criteria: ``(((((((((Bacterial
Microbiome) AND (Obesity or bmi or body mass index or BMI or obesity)
AND''last 10 years``{[}PDat{]} AND Humans{[}Mesh{]})) NOT
review{[}ptyp{]}) AND''last 10 years``{[}PDat{]} AND Humans{[}Mesh{]}))
AND''last 10 years``{[}PDat{]} AND Humans{[}Mesh{]})) AND''last 10
years``{[}PDat{]} AND Humans{[}Mesh{]})''. The terms included in this
criteria were that the manuscript had to have ``Bacterial Microbiome''
and ``Obesity, BMI, bmi, obesity'' in their manuscript criteria, it was
not published more than 10 years ago, they were not review articles, and
it contained research on humans only. This search yielded a total of 187
manuscripts. From the Finucane and Walters re-analysis studies along
with knowledge of other published papers that included BMI information
in their sequence metadata we obtained 10 additional studies. This
brought our total number of records to 197. We browsed abstracts of
these studies and included studies that mentioned stool or feces
examination, did not involve children, was not a clinical trial for
probiotics or other diet related treatments, did not have participants
with inflammatory bowel disease, were in English, and were based on the
analysis of sequence data from the 454 or MiSeq platforms. This
ultimately excluded all but a total of 11 studies. Because we decided
\emph{a priori} to use the standard definition for BMI group
classification one study was excluded because it did not have any
individuals who were obese.
